Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
Updated synthesis process overview.

%------------------------------------
\subsection{DSVerifier Verification Flow}
\label{verification-flow}
%------------------------------------

@@

The DSVerifier verification flow is illustrated in Fig.~\ref{DSVerifier_process};
a detailed description of DSVerifier tool can be found in~\cite{IsmailBCFF15}.
Steps $1$ to $5$ are performed by the user/synthesiser and
Steps A to D are automatically performed by DSVerifier.
%, which accepts the
%digital controller transfer functions together with the plant model.  For
%any digital controller, implementation details should be provided ({\it
%e.g.}, number of bits, realization, and sample time).

@@

This intermediate ANSI-C code model $(\tilde C(z),\mathfrak{G}(z),\phi)$
containing a specification $\phi$ for the verification properties ({\it
i.e.}, robust stability) is translated into SAT/SMT formulae by a back-end
model-checking tool ({\it e.g.}, CBMC~\cite{ClarkeKL04} or
ESBMC~\cite{CordeiroFM12}).  If any property violation is found, then
DSVerifier reports a counterexample, which contains system inputs or
parametric deviations $\Delta{G}$ that lead the system to a failure.  A
successful verification result is reported if the system is safe with
respect to $\phi$.  In particular, the stability verification is complete
and sound, since it does not depend on system inputs and outputs.  In the
case of stability, the specification $\phi$ consists in a number of
assumptions on the polynomial coefficients, following Jury's Criteria, as
well as the restrictions set in the representation of these coefficients by
the function $f$ (cf.~Eq.~\eqref{FWL_tf}).

\textcolor{red}{Pascal: can you please update this section to include the CEGIS step?}

@@

\subsection{General architecture of the program synthesiser}
%
%% \red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
%% (Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
% 
The input specification provided to the program synthesiser is of the
form $\exists \vec{P} . \forall \vec{x}. \sigma(\vec{x}, \vec{P})$ where $\vec{P}$ ranges over functions,
$\vec{x}$ ranges over ground terms and $\sigma$ is a quantifier-free
formula.  We interpret the ground terms over some finite domain
$\mathcal{D}$.

>>>>

%------------------------------------
\subsection{Synthesis Process using DSVerifier}
\label{verification-flow}
%------------------------------------

@@

The full synthesis process is illustrated in Fig.~\ref{DSVerifier_process};
a detailed description of DSVerifier tool can be found in~\cite{IsmailBCFF15}.
Steps $1$ to $5$ are performed by the user/synthesiser and
Steps A to D are automatically performed by DSVerifier.
%, which accepts the
%digital controller transfer functions together with the plant model.  For
%any digital controller, implementation details should be provided ({\it
%e.g.}, number of bits, realization, and sample time).

@@

This intermediate ANSI-C code model $(\tilde C(z),\mathfrak{G}(z),\phi)$
containing a specification $\phi$ for the verification properties ({\it
i.e.}, robust stability) is provided to CBMC's~\cite{ClarkeKL04} integrated
CEGIS synthesis module, where $\tilde C(z)$ is marked as input variable to
synthesise.  If any property violation is found, then
a counterexample is reported, which contains system inputs or
parametric deviations $\Delta{G}$ that lead the system to a failure.  
This information allows the CEGIS module to refine its search for a stable
controller, which we explain in detail in section~\ref{synthesiser-general}.
A successful verification result is reported if the system is safe with
respect to $\phi$.  In particular, the stability verification is complete
and sound, since it does not depend on system inputs and outputs.  In the
case of stability, the specification $\phi$ consists in a number of
assumptions on the polynomial coefficients, following Jury's Criteria, as
well as the restrictions set in the representation of these coefficients by
the function $f$ (cf.~Eq.~\eqref{FWL_tf}).

@@

\subsection{General architecture of the program synthesiser}
\label{synthesiser-general}
%
%% \red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
%% (Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
% 
The input specification provided to the program synthesiser is of the
form $\exists \vec{P} . \forall \vec{x}. \sigma(\vec{x}, \vec{P})$ where $\vec{P}$ ranges over functions,
$\vec{x}$ ranges over ground terms and $\sigma$ is a quantifier-free
formula.  We interpret the ground terms over some finite domain
$\mathcal{D}$.
